\mutagen: Coverage-Guided, Property-Based Testing using Exhaustive Type-Preserving Mutations

### 2021-04-16 papers/oopsla-21/main.tex
Improved sentence

%Instead of continuously generating random invalid test cases from scratch,
\fuzzchick keeps a queue of interesting previously executed test cases that can
be mutated using high-level, type-preserving transformations to produce new
ones.
%
Intuitively, mutating an interesting test case in a small way (at the data
constructor level) has a much higher probability of producing a new interesting
test case than generating a new one from scratch using a na\"ive generator.
%
In this light, \fuzzchick is likely to preserve the semantic structure of the
mutated data, as mutations are applied directly at the data type level, e.g.,
the program's AST in case of generating code.
%
Internally, \fuzzchick relies on execution traces to distinguish which executed
test cases were interesting and are therefore worth mutating --- a popular
technique known as \emph{coverage-guided fuzzing} and popularized by tools like
\emph{AFL} \cite{afl}.
%
Mutated test cases are considered interesting for mutation only when they
produce new execution traces --- any other test case is simply thrown away.
%
The techniques behind \fuzzchick are not meant to replace sophisticated,
manually written random generators, but rather to provide an adequate testing
solution for early stages of development.
%, and while a better test suite using manually-written generators is
%still under construction.

>>>>

%Instead of continuously generating random invalid test cases from scratch,
\fuzzchick keeps a queue of interesting previously executed test cases that can
be mutated using high-level, type-preserving transformations to produce new
ones.
%
Intuitively, mutating an interesting test case in a small way (at the data
constructor level) has a much higher probability of producing a new interesting
test case than generating a new one from scratch using a na\"ive generator.
%
In this light, \fuzzchick is likely to preserve the semantic structure of the
mutated data, as mutations are applied directly at the data type level, e.g.,
the program's AST in case of generating code.
%
Internally, \fuzzchick relies on execution traces to distinguish which executed
test cases were interesting and are therefore worth mutating --- a popular
technique known as \emph{coverage-guided fuzzing} and popularized by tools like
\emph{AFL} \cite{afl}.
%
Mutated test cases are considered interesting for mutation only when they
produce new execution traces --- any other test case is simply thrown away.
%
Worth mentioning, the techniques behind \fuzzchick are not meant to replace
sophisticated, manually written random generators, but rather to provide an
adequate testing solution for early stages of development.
%, and while a better test suite using manually-written generators is
%still under construction.
